\documentclass{cernatsnote}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{placeins}
\usepackage{siunitx}
\usepackage{soul}
\usepackage{bytefield}
\usepackage{tikz-timing}


\newcolumntype{?}{!{\vrule width 2pt}}

\usepackage{svg}
\svgsetup{
    inkscape=pdf,
    inkscapeexe={C:/inkscape.exe.lnk -z -C"}
}
\graphicspath{{images/}}

\usepackage[per-mode=symbol,separate-uncertainty=true]{siunitx}

\title{FastIC+ readout in-depth description}
\author{
	Vojtech Vosahlo \; \\		
	CERN, CH-1211 Geneva, Switzerland
}
\email{vojtech.vosahlo@cern.ch}
\date{\today}

\DeclareSIUnit\bit{b}

\begin{document}
\maketitle

\begin{abstract}
This document aims to describe the concept and working principles of the FastIC+ readout. To do so, it first introduces the FastIC+ chip itself. Afterwards, it focuses on the Aurora protocol, it's packet structure and the structure of the FastIC+ packets. Than, the main ideas behind receiving the data stream with an microcontroller are presented. Last but not least, each block of the system is described in detail.
\end{abstract}
\\ \\ \\ 

\newpage
\begingroup
\color{black}
\tableofcontents
\endgroup

\pagebreak

\section{Introduction}
In order to enhance the time measurement of the ToA and ToT analog pulses, FastIC+ has added a picosecond TDC for digitizing the pulses on the chip itself. This, in turn, has necessitated the need for a high-speed communication channel capable of transferring the resulting data stream. The Aurora 64B/66B protocol was chosen for its sufficient speed and easy interfacing with FPGAs.


\include{fastic}
\include{aurora}
\include{fastic_com}
\include{electronics}



\clearpage
\FloatBarrier
\bibliography{references}
\bibliographystyle{plain}

\end{document}